### 2021-05-18 chatbot_classification/03.emnlp_2021/appendix.tex
modified:   appendix.tex   modified:   experiments.tex

\subsection{Implementation Details}
For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
classification  task  and  sentence-pair similarity task. We fine-tune
our  SFC  system  on  our datasets with max sequence length of 128,
learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.

In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
for  giving  task  2 relatively more weights is that according to the ablation
experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
overall  performance.  In  joint-SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
in joint-SFC than in two-stage SFC.

For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
SFC system under various hyperparameter settings.

As for the training time, in our settings, our joint-SFC model needs about 14
hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
needs about 12 hours, which indicates that our joint-SFC model spends less training
time than the summation of two baseline models due to faster convergence.

As for the inference time, the classification model baseline is about 0.2 ms;
the similarity model baseline is about 0.5 ms and our joint-SFC model takes only 0.6 ms.
Actually both the similarity model baseline and our joint-SFC can be GPU
parallelized in the similarity computation, if we need pretty fast response time
in a real product.

>>>>

\subsection*{Relation to the label embedding based LEAM}
LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.

LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
One candidate solution is setting a most standard sample as the label of the class. 
When using non-pretrained models base LEAM, this is applicable. 
Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.

Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   appendix.tex   modified:   experiments.tex

\subsubsection*{Relation to the label embedding based LEAM}
LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.

LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
One candidate solution is setting a most standard sample as the label of the class. 
When using non-pretrained models base LEAM, this is applicable. 
Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.

Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.

>>>>

\subsection{Implementation Details}
For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
classification  task  and  sentence-pair similarity task. We fine-tune
our  SFC  system  on  our datasets with max sequence length of 128,
learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.

In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
for  giving  task  2 relatively more weights is that according to the ablation
experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
overall  performance.  In  joint-SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
in joint-SFC than in two-stage SFC.

For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
SFC system under various hyperparameter settings.

As for the training time, in our settings, our joint-SFC model needs about 14
hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
needs about 12 hours, which indicates that our joint-SFC model spends less training
time than the summation of two baseline models due to faster convergence.

As for the inference time, the classification model baseline is about 0.2 ms;
the similarity model baseline is about 0.5 ms and our joint-SFC model takes only 0.6 ms.
Actually both the similarity model baseline and our joint-SFC can be GPU
parallelized in the similarity computation, if we need pretty fast response time
in a real product.
